---
title: "1. Downloading and Preparing the Data for Cleaning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# setwd("~/Desktop/Columbia/Frameworks & Methods II/Project")
```

```{r}
library(lubridate)
library(devtools)
library(RedditExtractoR)
library(data.table)
library(dplyr)
library(tidyquant)
library(gtrendsR)
library(stringr)
library(tm)
library(ggplot2)
library(tidytext)
library(mice)
```

DOWNLOADING DATA AND PREPARING DATA FOR CLEANING

Downloading Reddit data - this was done twice, on February 2nd, and on April 18th. As the data one is able to download using the API is only for a month (at least on all of our laptops), we had a gap for the period of March 2nd to March 17th, which we aimed to fill using alternative methods.

Therefore, the three datasets are for the following periods:
  1. February 2nd, 2022 - March 1st, 2022;
  2. March 2nd, 2022 - March 17th, 2022 (using an alternative method);
  3. March 18th, 2022 - April 18th, 2022.

For 1 and 3, find the code used below:
```{r}
eth <- find_thread_urls(subreddit = "Ethereum", sort_by = "new", period = "month") # Downloads most recent posts going back one month from today.
eth_content <- get_thread_content(eth$url)

str(eth_content)
```

Preparing the data for analysis.
Step 1: separating the list of data frames to separate data frames.
```{r}
threads <- eth_content[-2];
comments <- eth_content[-1];

threads <- as.data.frame(threads)
comments <- as.data.frame(comments)

str(threads)
str(comments)
```

Step 2: dropping unnecessary columns.
```{r}
comments <- comments %>% select(c("comments.url", "comments.date", "comments.score", "comments.comment"))
```

Step 3: combining the two data frames into one for easier cleaning and analysis using URL as the unique identifier.
```{r}
comments <- comments %>% mutate(threads.title = threads$threads.title[match(comments$comments.url, threads$threads.url)])

comments <- comments %>% mutate(threads.text = threads$threads.text[match(comments$comments.url, threads$threads.url)])

comments <- comments %>% mutate(threads.score = threads$threads.score[match(comments$comments.url, threads$threads.url)])
```

Saving the files as CSVs:
```{r}
# fwrite(comments, 'ETH.csv')
```



SECOND DATASET
For the second period of the dataset, the following code was used:
```{r}
devtools::install_github("https://github.com/nathancunn/pushshiftR", force = TRUE)
```

I'm sure a for loop or couple would have been very useful here, but I am rather uncomfortable writing them in R as opposed to Python, so I just edited the code manually:

03/02
```{r}
eth_sub_0302 = pushshiftR::getPushshiftData(postType = "submission",
                                            size = 1000,
                                            after = "1646179200",
                                            before = "1646265600",
                                            subreddit = "Ethereum")

eth_com_0302 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646179200",
                                        before = "1646265600",
                                        subreddit = "Ethereum")

eth_sub_0302$created_utc <- as_date(as_datetime(eth_sub_0302$created_utc))
eth_sub_0302$created_utc

eth_com_0302$created_utc <- as_date(as_datetime(eth_com_0302$created_utc))
eth_com_0302$created_utc
```

03/03
```{r}
eth_sub_0303 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646265600",
                                        before = "1646352000",
                                        subreddit = "Ethereum")

eth_com_0303 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646265600",
                                        before = "1646352000",
                                        subreddit = "Ethereum")

eth_sub_0303$created_utc <- as_date(as_datetime(eth_sub_0303$created_utc))
eth_sub_0303$created_utc

eth_com_0303$created_utc <- as_date(as_datetime(eth_com_0303$created_utc))
eth_com_0303$created_utc
```

03/04
```{r}
eth_sub_0304 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646352000",
                                        before = "1646438400",
                                        subreddit = "Ethereum")

eth_com_0304 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646352000",
                                        before = "1646438400",
                                        subreddit = "Ethereum")

eth_sub_0304$created_utc <- as_date(as_datetime(eth_sub_0304$created_utc))
eth_sub_0304$created_utc

eth_com_0304$created_utc <- as_date(as_datetime(eth_com_0304$created_utc))
eth_com_0304$created_utc
```

03/05
```{r}
eth_sub_0305 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646438400",
                                        before = "1646524800",
                                        subreddit = "Ethereum")

eth_com_0305 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646438400",
                                        before = "1646524800",
                                        subreddit = "Ethereum")

eth_sub_0305$created_utc <- as_date(as_datetime(eth_sub_0305$created_utc))
eth_sub_0305$created_utc

eth_com_0305$created_utc <- as_date(as_datetime(eth_com_0305$created_utc))
eth_com_0305$created_utc
```

03/06
```{r}
eth_sub_0306 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646524800",
                                        before = "1646611200",
                                        subreddit = "Ethereum")

eth_com_0306 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646524800",
                                        before = "1646611200",
                                        subreddit = "Ethereum")

eth_sub_0306$created_utc <- as_date(as_datetime(eth_sub_0306$created_utc))
eth_sub_0306$created_utc

eth_com_0306$created_utc <- as_date(as_datetime(eth_com_0306$created_utc))
eth_com_0306$created_utc
```

03/07
```{r}
eth_sub_0307 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646611200",
                                        before = "1646697600",
                                        subreddit = "Ethereum")

eth_com_0307 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646611200",
                                        before = "1646697600",
                                        subreddit = "Ethereum")

eth_sub_0307$created_utc <- as_date(as_datetime(eth_sub_0307$created_utc))
eth_sub_0307$created_utc

eth_com_0307$created_utc <- as_date(as_datetime(eth_com_0307$created_utc))
eth_com_0307$created_utc
```

03/08
```{r}
eth_sub_0308 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646697600",
                                        before = "1646784000",
                                        subreddit = "Ethereum")

eth_com_0308 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646697600",
                                        before = "1646784000",
                                        subreddit = "Ethereum")

eth_sub_0308$created_utc <- as_date(as_datetime(eth_sub_0308$created_utc))
eth_sub_0308$created_utc

eth_com_0308$created_utc <- as_date(as_datetime(eth_com_0308$created_utc))
eth_com_0308$created_utc
```

03/09
```{r}
eth_sub_0309 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646784000",
                                        before = "1646870400",
                                        subreddit = "Ethereum")

eth_com_0309 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646784000",
                                        before = "1646870400",
                                        subreddit = "Ethereum")

eth_sub_0309$created_utc <- as_date(as_datetime(eth_sub_0309$created_utc))
eth_sub_0309$created_utc

eth_com_0309$created_utc <- as_date(as_datetime(eth_com_0309$created_utc))
eth_com_0309$created_utc
```

03/10
```{r}
eth_sub_0310 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646870400",
                                        before = "1646956800",
                                        subreddit = "Ethereum")

eth_com_0310 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646870400",
                                        before = "1646956800",
                                        subreddit = "Ethereum")

eth_sub_0310$created_utc <- as_date(as_datetime(eth_sub_0310$created_utc))
eth_sub_0310$created_utc

eth_com_0310$created_utc <- as_date(as_datetime(eth_com_0310$created_utc))
eth_com_0310$created_utc
```

03/11
```{r}
eth_sub_0311 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1646956800",
                                        before = "1647043200",
                                        subreddit = "Ethereum")

eth_com_0311 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1646956800",
                                        before = "1647043200",
                                        subreddit = "Ethereum")

eth_sub_0311$created_utc <- as_date(as_datetime(eth_sub_0311$created_utc))
eth_sub_0311$created_utc

eth_com_0311$created_utc <- as_date(as_datetime(eth_com_0311$created_utc))
eth_com_0311$created_utc
```

03/12
```{r}
eth_sub_0312 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1647043200",
                                        before = "1647129600",
                                        subreddit = "Ethereum")

eth_com_0312 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1647043200",
                                        before = "1647129600",
                                        subreddit = "Ethereum")

eth_sub_0312$created_utc <- as_date(as_datetime(eth_sub_0312$created_utc))
eth_sub_0312$created_utc

eth_com_0312$created_utc <- as_date(as_datetime(eth_com_0312$created_utc))
eth_com_0312$created_utc
```

03/13
```{r}
eth_sub_0313 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1647129600",
                                        before = "1647216000",
                                        subreddit = "Ethereum")

eth_com_0313 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1647129600",
                                        before = "1647216000",
                                        subreddit = "Ethereum")

eth_sub_0313$created_utc <- as_date(as_datetime(eth_sub_0313$created_utc))
eth_sub_0313$created_utc

eth_com_0313$created_utc <- as_date(as_datetime(eth_com_0313$created_utc))
eth_com_0313$created_utc
```

03/14
```{r}
eth_sub_0314 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1647216000",
                                        before = "1647302400",
                                        subreddit = "Ethereum")

eth_com_0314 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1647216000",
                                        before = "1647302400",
                                        subreddit = "Ethereum")

eth_sub_0314$created_utc <- as_date(as_datetime(eth_sub_0314$created_utc))
eth_sub_0314$created_utc

eth_com_0314$created_utc <- as_date(as_datetime(eth_com_0314$created_utc))
eth_com_0314$created_utc
```

03/15
```{r}
eth_sub_0315 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1647302400",
                                        before = "1647388800",
                                        subreddit = "Ethereum")

eth_com_0315 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1647302400",
                                        before = "1647388800",
                                        subreddit = "Ethereum")

eth_sub_0315$created_utc <- as_date(as_datetime(eth_sub_0315$created_utc))
eth_sub_0315$created_utc

eth_com_0315$created_utc <- as_date(as_datetime(eth_com_0315$created_utc))
eth_com_0315$created_utc
```

03/16
```{r}
eth_sub_0316 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1647388800",
                                        before = "1647475200",
                                        subreddit = "Ethereum")

eth_com_0316 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1647388800",
                                        before = "1647475200",
                                        subreddit = "Ethereum")

eth_sub_0316$created_utc <- as_date(as_datetime(eth_sub_0316$created_utc))
eth_sub_0316$created_utc

eth_com_0316$created_utc <- as_date(as_datetime(eth_com_0316$created_utc))
eth_com_0316$created_utc
```

03/17
```{r}
eth_sub_0317 = pushshiftR::getPushshiftData(postType = "submission",
                                        size = 1000,
                                        after = "1647475200",
                                        before = "1647561600",
                                        subreddit = "Ethereum")

eth_com_0317 = pushshiftR::getPushshiftData(postType = "comment",
                                        size = 1000,
                                        after = "1647475200",
                                        before = "1647561600",
                                        subreddit = "Ethereum")

eth_sub_0317$created_utc <- as_date(as_datetime(eth_sub_0317$created_utc))
eth_sub_0317$created_utc

eth_com_0317$created_utc <- as_date(as_datetime(eth_com_0317$created_utc))
eth_com_0317$created_utc
```

Merging all of the data frames into comment and thread data frames:
```{r}
comments = rbind(eth_com_0302,
                 eth_com_0303,
                 eth_com_0304,
                 eth_com_0305,
                 eth_com_0306,
                 eth_com_0307,
                 eth_com_0308,
                 eth_com_0309,
                 eth_com_0310,
                 eth_com_0311,
                 eth_com_0312,
                 eth_com_0313,
                 eth_com_0314,
                 eth_com_0315,
                 eth_com_0316,
                 eth_com_0317)

threads = rbind(eth_sub_0302,
                eth_sub_0303,
                eth_sub_0304,
                eth_sub_0305,
                eth_sub_0306,
                eth_sub_0307,
                eth_sub_0308,
                eth_sub_0309,
                eth_sub_0310,
                eth_sub_0311,
                eth_sub_0312,
                eth_sub_0313,
                eth_sub_0314,
                eth_sub_0315,
                eth_sub_0316,
                eth_sub_0317)
```

Merging the two data frames by id and parent_id:
```{r}
comments$id <- str_sub(comments$parent_id, 4, -1)

comments <- comments %>% mutate(threads_title = threads$title[match(comments$id, threads$id)])
comments <- comments %>% mutate(threads_text = threads$selftext[match(comments$id, threads$id)])

eth_0302_0317 <- comments %>% select(c("created_utc", "threads_title", "threads_text", "body"))
```

Removing NAs:
```{r}
eth_0302_0317$body <- eth_0302_0317$body %>% na_if("[removed]")
eth_0302_0317 <- na.omit(eth_0302_0317)
```

Saving the file as a CSV:
```{r}
#fwrite(eth_0302_0317, 'ETH March Gap Dataframe.csv')
```



MERGING THE DATA
Finally, merging all of the datasets together:
```{r}
data1 = read.csv("ETH 1.csv")
data2 = read.csv("ETH 2.csv")
data3 = read.csv("ETH 3.csv")
```

Issues with the datasets:
  1) The date format of data1 and data3 differs from that of data2, yet each of the variables are characters.
  2) data2 is missing a comments.url column, which will be removed, as it was solely used for merging the threads to the comments.
  3) data 2 is missing comments.score and threads.score columns, data for which will me imputed using the MICE package.

Fixing the date issue:
```{r}
data1$comments.date <- as.Date(data1$comments.date, format =  "%m/%d/%y", tryFormats = "%Y-%m-%d")
data3$comments.date <- as.Date(data3$comments.date, format =  "%m/%d/%y", tryFormats = "%Y-%m-%d")

data2$created_utc <- as_date(data2$created_utc)
```

Removing the url columns from both data1 and data2:
```{r}
data1 <- data1 %>% select(!"comments.url")
data3 <- data3 %>% select(!"comments.url")
```

Merging the data sets into one data frame:
```{r}
# Renaming columns
colnames(data1) <- c("date", "commentScore", "comment", "threadTitle", "threadText", "threadScore")
colnames(data3) <- c("date", "commentScore", "comment", "threadTitle", "threadText", "threadScore")

colnames(data2) <- c("date", "threadTitle", "threadText", "comment")

# Adding two empty columns for commentScore and threadScore in data2:
data2[, c('commentScore', 'threadScore')] = NA

# Reordering columns
data1 <- data1[, c("date", "comment", "commentScore", "threadTitle", "threadText", "threadScore")]
data3 <- data2[, c("date", "comment", "commentScore", "threadTitle", "threadText", "threadScore")]

data2 <- data2[, c("date", "comment", "commentScore", "threadTitle", "threadText", "threadScore")]

data <- rbind(data1,
              data2,
              data3)
```

Imputing the missing variables:
```{r}
set.seed(10025)
data = mice::complete(mice(data, use.matcher=T))
```



Downloading the price of ETH for the period:
```{r}
eth = c("ETH-USD")

eth_price = tq_get(eth,
                   get = 'stock.prices',
                   from = "2022-02-02",
                   to = "2022-04-18")

eth_price = eth_price %>%
  select(-"symbol")

eth_price = as.data.frame(eth_price)
```

Matching the price of ETH to the comments by date:
```{r}
data <- data %>% mutate(price = eth_price$adjusted[match(data$date, eth_price$date)])
```

Downloading Google Trends data for ETH:
```{r}
thaler_google = gtrends(keyword = 'Ethereum', geo = c('US'), time = '2022-02-02 2022-04-18')
```

Selecting the relevant data frame for analysis, i.e. interest_over_time:
```{r}
thaler_google <- thaler_google[1]
thaler_google <- as.data.frame(thaler_google)
```

Matching the frequency of hits to the comments by date:
```{r}
thaler_google$interest_over_time.date <- as_date(thaler_google$interest_over_time.date)

data <- data %>% mutate(hits = thaler_google$interest_over_time.hits[match(data$date, thaler_google$interest_over_time.date)])
```

Saving the merged and complete file as CSV to be used for cleaning:
```{r}
# fwrite(data, 'ETH Complete Dataframe.csv')
```
